On Star Formation at Dynamical Resonances of the Bar

### 2019-12-06 paper/ms.tex
Update ms.tex
Updates to paper

% Abstract of the paper
\begin{abstract}
Stars are known to be captured at the dynamical resonances of the Milky Way
bar, forming moving groups that are seen in the solar neighborhood. In
principle, gas can also be captured at these resonances which, if allowed to
cool, might trigger star formation -- predicting an enhanced number of
star-forming regions at these resonances. However, the efficiency of stellar
and radiation feedback may suppress the star formation process.
\end{abstract}

@@

\section{Introduction}

>>>>

% Abstract of the paper
\begin{abstract}
Effective models

Stars are known to be captured at the dynamical resonances of the Milky Way
bar, forming moving groups that are seen in the solar neighborhood. In
principle, gas can also be captured at these resonances which, if allowed to
cool, might trigger star formation -- predicting an enhanced number of
star-forming regions at these resonances. However, the efficiency of stellar
and radiation feedback may suppress the star formation process. 
\end{abstract}

@@

\section{Introduction}
Due to issues of large dynamic range, effective models of star formation is a
crucial element of both high- and low-resolution numerical simulations of
galaxy formation.
